---
title: "Chenyi_writeup"
output: html_document
date: "2022-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(geojsonio)
library(ggplot2)
library(dplyr)
library(spdplyr)
library(tigris)
library(RColorBrewer)
```

### Read in data from .csv files

```{r load-data, message = FALSE}

feb_2019 <- read.csv("data/broadband_data_february_2019.csv")
aug_2019 <- read.csv("data/broadband_data_august_2019.csv")
gdhi_region <- read.csv("data/gdhi_per_region.csv", skip = 1)

```

### Tidy the datasets to make them easier to use

```{r clean-data}
feb_2019 <- feb_2019 %>%
  clean_names() %>%
  select(-ofcom_product) %>%    # These steps are to make the columns match the August dataset.
  rename("distance_from_exchange" = "distance_from_exchange_band")
  
aug_2019 <- aug_2019 %>%
  clean_names()

regions <- c("United Kingdom", "England", "North East", "North West", "Yorkshire & Humber", "East Midlands", 
             "West Midlands", "East", "London", "South East", "South West", "Wales", "Scotland", "Northern Ireland")

gdhi_region <- gdhi_region %>%
  clean_names() %>%
  drop_na() %>%
  rename("region" = "countries_and_regions_of_the_uk") %>%
  mutate(region = regions,
         gdhi_per_head = str_remove_all(gdhi_per_head, ","),
         gdhi_per_head = as.numeric(gdhi_per_head)
         )

aug_2019_month <- aug_2019 %>%
  mutate(month = "August")

all_2019 <- feb_2019 %>%
  mutate(month = "February") %>%
  rbind(aug_2019_month)

# Join datasets with gdhi_region set
feb_gdhi_join <- left_join(feb_2019, gdhi_region , by = "region")
aug_gdhi_join <- left_join(aug_2019, gdhi_region , by = "region")
all_gdhi_join <- left_join(all_2019, gdhi_region , by = "region")

```

### Graphs of internet quality factors against variables effect

```{r x24h_adv vs region}
ggplot(data = all_gdhi_join, 
       aes(x = region, y = x24_hr_average_download_speed, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  geom_smooth(formula = y~x, method = "lm", se = FALSE, fullrange = TRUE) +
  labs(
    title = "Regions effect 24h average download speed, by urban/rural features",
    x = "regions in UK",
    y = "24h download speed",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip()
```
```{r x24h_adv vs def}
feb_2019_dfe_plot <- feb_2019 %>%
  drop_na() %>%
  mutate(
    distance_from_exchange = case_when(
      distance_from_exchange == "0 to 100m" ~ "01",
      distance_from_exchange == "101 to 200m" ~ "02",
      distance_from_exchange == "201 to 300m" ~ "03",
      distance_from_exchange == "301 to 400m" ~ "04",
      distance_from_exchange == "401 to 500m" ~ "05",
      distance_from_exchange == "501 to 600m" ~ "06",
      distance_from_exchange == "601 to 700m" ~ "07",
      distance_from_exchange == "701 to 800m" ~ "08",
      distance_from_exchange == "801 to 900m" ~ "09",
      distance_from_exchange == "901 to 1000m" ~ "10",
      distance_from_exchange == "1001 to 1100m" ~ "11",
      distance_from_exchange == "1101 to 1200m" ~ "12",
      distance_from_exchange == "1201 to 1300m" ~ "13",
      distance_from_exchange == "1301 to 1400m" ~ "14",
      distance_from_exchange == "1401 to 1500m" ~ "15",
      distance_from_exchange == "1501 to 1600m" ~ "16",
      distance_from_exchange == "1601 to 1700m" ~ "17",
      distance_from_exchange == "1701 to 1800m" ~ "18",
      distance_from_exchange == "1801 to 1900m" ~ "19",
      distance_from_exchange == "1901 to 2000m" ~ "20",
      distance_from_exchange == "2001 to 2100m" ~ "21",
      distance_from_exchange == "2101 to 2200m" ~ "22",
      distance_from_exchange == "2201 to 2300m" ~ "23",
      distance_from_exchange == "2301 to 2400m" ~ "24",
      distance_from_exchange == "2401 to 2500m" ~ "25",
      distance_from_exchange == "2501 to 2600m" ~ "26",
      distance_from_exchange == "2601 to 2700m" ~ "27",
      distance_from_exchange == "2701 to 2800m" ~ "28",
      distance_from_exchange == "2801 to 2900m" ~ "29",
      distance_from_exchange == "2901 to 3000m" ~ "30",
      distance_from_exchange == "3001 to 3250m" ~ "31",
      distance_from_exchange == "3251 to 3500m" ~ "32",
      distance_from_exchange == "3501 to 3750m" ~ "33",
      distance_from_exchange == "3751 to 4000m" ~ "34",
      distance_from_exchange == "4001 to 4500m" ~ "35",
      distance_from_exchange == "4501 to 5000m" ~ "36",
      distance_from_exchange == "5001 to 5500m" ~ "37",
      distance_from_exchange == "Over 5500m" ~ "38"
    ))
aug_2019_dfe_plot <- aug_2019 %>%
  drop_na() %>%
  mutate(
    distance_from_exchange = case_when(
      distance_from_exchange == "0 to 100m" ~ "01",
      distance_from_exchange == "101 to 200m" ~ "02",
      distance_from_exchange == "201 to 300m" ~ "03",
      distance_from_exchange == "301 to 400m" ~ "04",
      distance_from_exchange == "401 to 500m" ~ "05",
      distance_from_exchange == "501 to 600m" ~ "06",
      distance_from_exchange == "601 to 700m" ~ "07",
      distance_from_exchange == "701 to 800m" ~ "08",
      distance_from_exchange == "801 to 900m" ~ "09",
      distance_from_exchange == "901 to 1000m" ~ "10",
      distance_from_exchange == "1001 to 1100m" ~ "11",
      distance_from_exchange == "1101 to 1200m" ~ "12",
      distance_from_exchange == "1201 to 1300m" ~ "13",
      distance_from_exchange == "1301 to 1400m" ~ "14",
      distance_from_exchange == "1401 to 1500m" ~ "15",
      distance_from_exchange == "1501 to 1600m" ~ "16",
      distance_from_exchange == "1601 to 1700m" ~ "17",
      distance_from_exchange == "1701 to 1800m" ~ "18",
      distance_from_exchange == "1801 to 1900m" ~ "19",
      distance_from_exchange == "1901 to 2000m" ~ "20",
      distance_from_exchange == "2001 to 2100m" ~ "21",
      distance_from_exchange == "2101 to 2200m" ~ "22",
      distance_from_exchange == "2201 to 2300m" ~ "23",
      distance_from_exchange == "2301 to 2400m" ~ "24",
      distance_from_exchange == "2401 to 2500m" ~ "25",
      distance_from_exchange == "2501 to 2600m" ~ "26",
      distance_from_exchange == "2601 to 2700m" ~ "27",
      distance_from_exchange == "2701 to 2800m" ~ "28",
      distance_from_exchange == "2801 to 2900m" ~ "29",
      distance_from_exchange == "2901 to 3000m" ~ "30",
      distance_from_exchange == "3001 to 3250m" ~ "31",
      distance_from_exchange == "3251 to 3500m" ~ "32",
      distance_from_exchange == "3501 to 3750m" ~ "33",
      distance_from_exchange == "3751 to 4000m" ~ "34",
      distance_from_exchange == "4001 to 4500m" ~ "35",
      distance_from_exchange == "4501 to 5000m" ~ "36",
      distance_from_exchange == "5001 to 5500m" ~ "37",
      distance_from_exchange == "Over 5500m" ~ "38"
    ))

aug_2019_dfe_plot_month <- aug_2019_dfe_plot %>%
  mutate(month = "August")
all_2019_dfe_plot <- feb_2019_dfe_plot %>%
  mutate(month = "February") %>%
  rbind(aug_2019_dfe_plot_month)

ggplot(data = all_2019_dfe_plot, 
       aes(x = distance_from_exchange, y = x24_hour_packet_loss, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  labs(
    title = "distance effects 24h download speed, by urban/rural features",
    x = "distance from exchange",
    y = "24h average download speed",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip() 
```
```{r x24h_packet_loss vs dfe}
ggplot(data = all_2019_dfe_plot, 
       aes(x = distance_from_exchange, y = x24_hour_packet_loss, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  labs(
    title = "distance effects 24h packet loss, by urban/rural features",
    x = "distance from exchange",
    y = "24h packet loss",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip()
```
```{r x24h_latency vs dfe}
ggplot(data = all_2019_dfe_plot, 
       aes(x = distance_from_exchange, y = x24_hour_latency, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  geom_smooth(formula = y~x, method = "lm", se = FALSE) +
  labs(
    title = "distance effects 24h latency, by urban/rural features",
    x = "distance from exchange",
    y = "24h latency",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip()
```

We assume that internet quality can be defined by average download speed, packet loss and latency on the internet in 24 hours. 
And they are influenced by geolocations that whether users are at urban or rural as well as their regions located in the UK and distance from the exchange.
We can see from the graphs that in rural areas, users generally experiened lower download speed, higher packet loss and higher latency. 
Also, for distance from exchange, since the categories of the variable is too long to be used and would cause disordered y-axis, I redefine them as a new simple category.