---
title: "Workshop Group 31/1 Project"
output: html_document
author: "Ryan Hall, Eddie Washbrook, Eric Rogers, Chenyi He, Zhihong Chen"
date: "2022-11-16"
---
# Do geographical location and characteristics have an effect on internet quality of life in the UK? An analysis of and comparison between two months in 2019

### Load required packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(geojsonio)
library(ggplot2)
library(dplyr)
library(spdplyr)
library(tigris)
library(RColorBrewer)
```

### Read in data from .csv files

```{r load-data, message = FALSE}

feb_2019 <- read.csv("data/broadband_data_february_2019.csv")
aug_2019 <- read.csv("data/broadband_data_august_2019.csv")
gdhi_region <- read.csv("data/gdhi_per_region.csv", skip = 1)

```

### Tidy the datasets to make them easier to use

```{r clean-data}
feb_2019 <- feb_2019 %>%
  clean_names() %>%
  select(-ofcom_product) %>%    # These steps are to make the columns match the August dataset.
  rename("distance_from_exchange" = "distance_from_exchange_band")
  
aug_2019 <- aug_2019 %>%
  clean_names()

regions <- c("United Kingdom", "England", "North East", "North West", "Yorkshire & Humber", "East Midlands", 
             "West Midlands", "East", "London", "South East", "South West", "Wales", "Scotland", "Northern Ireland")

gdhi_region <- gdhi_region %>%
  clean_names() %>%
  drop_na() %>%
  rename("region" = "countries_and_regions_of_the_uk") %>%
  mutate(region = regions,
         gdhi_per_head = str_remove_all(gdhi_per_head, ","),
         gdhi_per_head = as.numeric(gdhi_per_head)
         )

aug_2019_month <- aug_2019 %>%
  mutate(month = "August")

all_2019 <- feb_2019 %>%
  mutate(month = "February") %>%
  rbind(aug_2019_month)

# Join datasets with gdhi_region set
feb_gdhi_join <- left_join(feb_2019, gdhi_region , by = "region")
aug_gdhi_join <- left_join(aug_2019, gdhi_region , by = "region")
all_gdhi_join <- left_join(all_2019, gdhi_region , by = "region")

```

### Graphs of internet quality factors against variables effect

```{r x24h_adv vs region}
ggplot(data = all_gdhi_join, 
       aes(x = region, y = x24_hr_average_download_speed, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  geom_smooth(formula = y~x, method = "lm", se = FALSE, fullrange = TRUE) +
  labs(
    title = "Regions effect 24h average download speed, by urban/rural features",
    x = "regions in UK",
    y = "24h download speed",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip()
```
```{r x24h_adv vs def}
feb_2019_dfe_plot <- feb_2019 %>%
  drop_na() %>%
  mutate(
    distance_from_exchange = case_when(
      distance_from_exchange == "0 to 100m" ~ "01",
      distance_from_exchange == "101 to 200m" ~ "02",
      distance_from_exchange == "201 to 300m" ~ "03",
      distance_from_exchange == "301 to 400m" ~ "04",
      distance_from_exchange == "401 to 500m" ~ "05",
      distance_from_exchange == "501 to 600m" ~ "06",
      distance_from_exchange == "601 to 700m" ~ "07",
      distance_from_exchange == "701 to 800m" ~ "08",
      distance_from_exchange == "801 to 900m" ~ "09",
      distance_from_exchange == "901 to 1000m" ~ "10",
      distance_from_exchange == "1001 to 1100m" ~ "11",
      distance_from_exchange == "1101 to 1200m" ~ "12",
      distance_from_exchange == "1201 to 1300m" ~ "13",
      distance_from_exchange == "1301 to 1400m" ~ "14",
      distance_from_exchange == "1401 to 1500m" ~ "15",
      distance_from_exchange == "1501 to 1600m" ~ "16",
      distance_from_exchange == "1601 to 1700m" ~ "17",
      distance_from_exchange == "1701 to 1800m" ~ "18",
      distance_from_exchange == "1801 to 1900m" ~ "19",
      distance_from_exchange == "1901 to 2000m" ~ "20",
      distance_from_exchange == "2001 to 2100m" ~ "21",
      distance_from_exchange == "2101 to 2200m" ~ "22",
      distance_from_exchange == "2201 to 2300m" ~ "23",
      distance_from_exchange == "2301 to 2400m" ~ "24",
      distance_from_exchange == "2401 to 2500m" ~ "25",
      distance_from_exchange == "2501 to 2600m" ~ "26",
      distance_from_exchange == "2601 to 2700m" ~ "27",
      distance_from_exchange == "2701 to 2800m" ~ "28",
      distance_from_exchange == "2801 to 2900m" ~ "29",
      distance_from_exchange == "2901 to 3000m" ~ "30",
      distance_from_exchange == "3001 to 3250m" ~ "31",
      distance_from_exchange == "3251 to 3500m" ~ "32",
      distance_from_exchange == "3501 to 3750m" ~ "33",
      distance_from_exchange == "3751 to 4000m" ~ "34",
      distance_from_exchange == "4001 to 4500m" ~ "35",
      distance_from_exchange == "4501 to 5000m" ~ "36",
      distance_from_exchange == "5001 to 5500m" ~ "37",
      distance_from_exchange == "Over 5500m" ~ "38"
    ))
aug_2019_dfe_plot <- aug_2019 %>%
  drop_na() %>%
  mutate(
    distance_from_exchange = case_when(
      distance_from_exchange == "0 to 100m" ~ "01",
      distance_from_exchange == "101 to 200m" ~ "02",
      distance_from_exchange == "201 to 300m" ~ "03",
      distance_from_exchange == "301 to 400m" ~ "04",
      distance_from_exchange == "401 to 500m" ~ "05",
      distance_from_exchange == "501 to 600m" ~ "06",
      distance_from_exchange == "601 to 700m" ~ "07",
      distance_from_exchange == "701 to 800m" ~ "08",
      distance_from_exchange == "801 to 900m" ~ "09",
      distance_from_exchange == "901 to 1000m" ~ "10",
      distance_from_exchange == "1001 to 1100m" ~ "11",
      distance_from_exchange == "1101 to 1200m" ~ "12",
      distance_from_exchange == "1201 to 1300m" ~ "13",
      distance_from_exchange == "1301 to 1400m" ~ "14",
      distance_from_exchange == "1401 to 1500m" ~ "15",
      distance_from_exchange == "1501 to 1600m" ~ "16",
      distance_from_exchange == "1601 to 1700m" ~ "17",
      distance_from_exchange == "1701 to 1800m" ~ "18",
      distance_from_exchange == "1801 to 1900m" ~ "19",
      distance_from_exchange == "1901 to 2000m" ~ "20",
      distance_from_exchange == "2001 to 2100m" ~ "21",
      distance_from_exchange == "2101 to 2200m" ~ "22",
      distance_from_exchange == "2201 to 2300m" ~ "23",
      distance_from_exchange == "2301 to 2400m" ~ "24",
      distance_from_exchange == "2401 to 2500m" ~ "25",
      distance_from_exchange == "2501 to 2600m" ~ "26",
      distance_from_exchange == "2601 to 2700m" ~ "27",
      distance_from_exchange == "2701 to 2800m" ~ "28",
      distance_from_exchange == "2801 to 2900m" ~ "29",
      distance_from_exchange == "2901 to 3000m" ~ "30",
      distance_from_exchange == "3001 to 3250m" ~ "31",
      distance_from_exchange == "3251 to 3500m" ~ "32",
      distance_from_exchange == "3501 to 3750m" ~ "33",
      distance_from_exchange == "3751 to 4000m" ~ "34",
      distance_from_exchange == "4001 to 4500m" ~ "35",
      distance_from_exchange == "4501 to 5000m" ~ "36",
      distance_from_exchange == "5001 to 5500m" ~ "37",
      distance_from_exchange == "Over 5500m" ~ "38"
    ))

aug_2019_dfe_plot_month <- aug_2019_dfe_plot %>%
  mutate(month = "August")
all_2019_dfe_plot <- feb_2019_dfe_plot %>%
  mutate(month = "February") %>%
  rbind(aug_2019_dfe_plot_month)

ggplot(data = all_2019_dfe_plot, 
       aes(x = distance_from_exchange, y = x24_hour_packet_loss, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  labs(
    title = "distance effects 24h download speed, by urban/rural features",
    x = "distance from exchange",
    y = "24h average download speed",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip() 
```
```{r x24h_packet_loss vs dfe}
ggplot(data = all_2019_dfe_plot, 
       aes(x = distance_from_exchange, y = x24_hour_packet_loss, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  labs(
    title = "distance effects 24h packet loss, by urban/rural features",
    x = "distance from exchange",
    y = "24h packet loss",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip()
```
```{r x24h_latency vs dfe}
ggplot(data = all_2019_dfe_plot, 
       aes(x = distance_from_exchange, y = x24_hour_latency, colour = urban_rural)) +
  geom_point(alpha = 0.4) +
  geom_smooth(formula = y~x, method = "lm", se = FALSE) +
  labs(
    title = "distance effects 24h latency, by urban/rural features",
    x = "distance from exchange",
    y = "24h latency",
    color = "urban/rural"
  ) +
  scale_color_manual(values = c("#E48957", "#071381")) +
  coord_flip()
```

### Maps of regional variation
```{r maps, fig.height = 5, fig.width = 10, warning = FALSE}

region_map <- geojson_read("uk_regions.geojson", what = "sp") %>%
  rename(region = rgn19nm)

feb_avg <- feb_2019 %>%
  group_by(region) %>%
  summarise(mean_24hr = mean(x24_hr_average_download_speed))

feb_joined <- region_map %>%
  geo_join(feb_avg, by = "region", how = "left")

aug_avg <- aug_2019 %>%
  group_by(region) %>%
  summarise(mean_24hr = mean(x24_hr_average_download_speed))

aug_joined <- region_map %>%
  geo_join(aug_avg, by = "region", how = "left")

reds <- brewer.pal(9, "Reds")
blues <- brewer.pal(9, "Blues")
greens <- brewer.pal(9, "Greens")

class_feb <- cut(feb_joined$mean_24hr, 9)
col_feb <- reds[as.numeric(class_feb)]
plot(feb_joined, col = col_feb, main = "UK 24 hour average broadband speed by region, February 2019",
     sub = "Data from data.gov.uk")

class_aug <- cut(aug_joined$mean_24hr, 9)
col_aug <- reds[as.numeric(class_aug)]
plot(aug_joined, col = col_aug, main = "UK 24 hour average broadband speed by region, August 2019",
     sub = "Data from data.gov.uk")

gdhi_joined <- region_map %>%
  geo_join(gdhi_region, by = "region", how = "left")

class_gdhi <- cut(gdhi_joined$gdhi_per_head, 9)
col_gdhi <- blues[as.numeric(class_gdhi)]
plot(gdhi_joined, col = col_gdhi, main = "Gross disposable household income per region in the UK, 2019", 
     sub = "Data from ons.gov.uk")

disparity <- feb_2019 %>%
  group_by(region, urban_rural) %>%
  summarise(avg_24hr = mean(x24_hr_average_download_speed)) %>%
  pivot_wider(names_from = urban_rural, values_from = avg_24hr) %>%
  mutate(ratio = Urban/Rural)
  
disparity$ratio <- replace_na(disparity$ratio, 1)

disparity_joined <- region_map %>%
  geo_join(disparity, by = "region", how = "left")

class_disp <- cut(disparity_joined$ratio, 9)
col_disp <- greens[as.numeric(class_disp)]
plot(disparity_joined, col = col_disp, main = "Ratio of urban to rural download speeds in the UK, February 2019", 
     sub = "Data from data.gov.uk")
```


### Household Income vs 24 hour Download Speed - Feb
```{r income-24h_download}
feb_24h_ads_gdhi_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ gdhi_per_head, data = feb_gdhi_join) %>%
  tidy()
feb_24h_ads_gdhi_fit
```

### (USELESS)Residuals plot (Household Income vs 24 hour Download Speed - Feb)
```{r residuals_plot_income-24h_download}
feb_24h_ads_gdhi_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ gdhi_per_head, data = feb_gdhi_join)
feb_24h_ads_gdhi_fit_aug  <- augment(feb_24h_ads_gdhi_fit$fit)

ggplot(feb_24h_ads_gdhi_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted x24_hr_average_download_speed", y = "Residuals")
```


### Urban/Rural vs 24 hour Download Speed - Feb
```{r urbanrural-24h_download}
feb_24h_ads_ur_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ urban_rural, data = feb_gdhi_join) %>%
  tidy()
feb_24h_ads_ur_fit
```

### (USELESS)Residuals plot (Urban/Rural vs 24 hour Download Speed - Feb)
```{r residuals_urbanrural-24h_download}
feb_24h_ads_ur_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ urban_rural, data = feb_gdhi_join)
feb_24h_ads_ur_fit_aug  <- augment(feb_24h_ads_ur_fit$fit)

ggplot(feb_24h_ads_ur_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted x24_hr_average_download_speed", y = "Residuals")
```




### (feb)ads VS dfe
```{r ads VS dfe}
feb_2019_dfe <- feb_2019 %>%
  drop_na() %>%
  mutate(
    distance_from_exchange = case_when(
      distance_from_exchange == "0 to 100m" ~ "50",
      distance_from_exchange == "101 to 200m" ~ "150",
      distance_from_exchange == "201 to 300m" ~ "250",
      distance_from_exchange == "301 to 400m" ~ "350",
      distance_from_exchange == "401 to 500m" ~ "450",
      distance_from_exchange == "501 to 600m" ~ "550",
      distance_from_exchange == "601 to 700m" ~ "650",
      distance_from_exchange == "701 to 800m" ~ "750",
      distance_from_exchange == "801 to 900m" ~ "850",
      distance_from_exchange == "901 to 1000m" ~ "950",
      distance_from_exchange == "1001 to 1100m" ~ "1050",
      distance_from_exchange == "1101 to 1200m" ~ "1150",
      distance_from_exchange == "1201 to 1300m" ~ "1250",
      distance_from_exchange == "1301 to 1400m" ~ "1350",
      distance_from_exchange == "1401 to 1500m" ~ "1450",
      distance_from_exchange == "1501 to 1600m" ~ "1550",
      distance_from_exchange == "1601 to 1700m" ~ "1650",
      distance_from_exchange == "1701 to 1800m" ~ "1750",
      distance_from_exchange == "1801 to 1900m" ~ "1850",
      distance_from_exchange == "1901 to 2000m" ~ "1950",
      distance_from_exchange == "2001 to 2100m" ~ "2050",
      distance_from_exchange == "2101 to 2200m" ~ "2150",
      distance_from_exchange == "2201 to 2300m" ~ "2250",
      distance_from_exchange == "2301 to 2400m" ~ "2350",
      distance_from_exchange == "2401 to 2500m" ~ "2450",
      distance_from_exchange == "2501 to 2600m" ~ "2550",
      distance_from_exchange == "2601 to 2700m" ~ "2650",
      distance_from_exchange == "2701 to 2800m" ~ "2750",
      distance_from_exchange == "2801 to 2900m" ~ "2850",
      distance_from_exchange == "2901 to 3000m" ~ "2950",
      distance_from_exchange == "3001 to 3250m" ~ "3125",
      distance_from_exchange == "3251 to 3500m" ~ "3375",
      distance_from_exchange == "3501 to 3750m" ~ "3625",
      distance_from_exchange == "3751 to 4000m" ~ "3875",
      distance_from_exchange == "4001 to 4500m" ~ "4250",
      distance_from_exchange == "4501 to 5000m" ~ "4750",
      distance_from_exchange == "5001 to 5500m" ~ "5250",
      distance_from_exchange == "Over 5500m" ~ "5500"
    ))
feb_2019_dfe$distance_from_exchange <- as.numeric(as.character(feb_2019_dfe$distance_from_exchange))

feb_2019_ads_dfe <- feb_2019_dfe %>%
  select(distance_from_exchange, x24_hr_average_download_speed) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_ads = mean(x24_hr_average_download_speed)
  )

feb_2019_ads_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ads ~ distance_from_exchange, data = feb_2019_ads_dfe) %>%
  tidy()
feb_2019_ads_dfe_fit
```


### (feb)residual plot(ads VS dfe)
```{r residual plot(ads VS dfe)}
feb_2019_ads_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ads ~ distance_from_exchange, data = feb_2019_ads_dfe)
feb_2019_ads_dfe_fit_aug  <- augment(feb_2019_ads_dfe_fit$fit)

ggplot(feb_2019_ads_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_ads", y = "Residuals")
```


### (aug)ads VS dfe
```{r (aug)ads VS dfe}
aug_2019_dfe <- aug_2019 %>%
  drop_na() %>%
  mutate(
    distance_from_exchange = case_when(
      distance_from_exchange == "0 to 100m" ~ "50",
      distance_from_exchange == "101 to 200m" ~ "150",
      distance_from_exchange == "201 to 300m" ~ "250",
      distance_from_exchange == "301 to 400m" ~ "350",
      distance_from_exchange == "401 to 500m" ~ "450",
      distance_from_exchange == "501 to 600m" ~ "550",
      distance_from_exchange == "601 to 700m" ~ "650",
      distance_from_exchange == "701 to 800m" ~ "750",
      distance_from_exchange == "801 to 900m" ~ "850",
      distance_from_exchange == "901 to 1000m" ~ "950",
      distance_from_exchange == "1001 to 1100m" ~ "1050",
      distance_from_exchange == "1101 to 1200m" ~ "1150",
      distance_from_exchange == "1201 to 1300m" ~ "1250",
      distance_from_exchange == "1301 to 1400m" ~ "1350",
      distance_from_exchange == "1401 to 1500m" ~ "1450",
      distance_from_exchange == "1501 to 1600m" ~ "1550",
      distance_from_exchange == "1601 to 1700m" ~ "1650",
      distance_from_exchange == "1701 to 1800m" ~ "1750",
      distance_from_exchange == "1801 to 1900m" ~ "1850",
      distance_from_exchange == "1901 to 2000m" ~ "1950",
      distance_from_exchange == "2001 to 2100m" ~ "2050",
      distance_from_exchange == "2101 to 2200m" ~ "2150",
      distance_from_exchange == "2201 to 2300m" ~ "2250",
      distance_from_exchange == "2301 to 2400m" ~ "2350",
      distance_from_exchange == "2401 to 2500m" ~ "2450",
      distance_from_exchange == "2501 to 2600m" ~ "2550",
      distance_from_exchange == "2601 to 2700m" ~ "2650",
      distance_from_exchange == "2701 to 2800m" ~ "2750",
      distance_from_exchange == "2801 to 2900m" ~ "2850",
      distance_from_exchange == "2901 to 3000m" ~ "2950",
      distance_from_exchange == "3001 to 3250m" ~ "3125",
      distance_from_exchange == "3251 to 3500m" ~ "3375",
      distance_from_exchange == "3501 to 3750m" ~ "3625",
      distance_from_exchange == "3751 to 4000m" ~ "3875",
      distance_from_exchange == "4001 to 4500m" ~ "4250",
      distance_from_exchange == "4501 to 5000m" ~ "4750",
      distance_from_exchange == "5001 to 5500m" ~ "5250",
      distance_from_exchange == "Over 5500m" ~ "5500"
    ))

aug_2019_dfe$distance_from_exchange <- as.numeric(as.character(aug_2019_dfe$distance_from_exchange))

aug_2019_ads_dfe <- aug_2019_dfe %>%
  select(distance_from_exchange, x24_hr_average_download_speed) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_ads = mean(x24_hr_average_download_speed)
  )

aug_2019_ads_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ads ~ distance_from_exchange, data = aug_2019_ads_dfe) %>%
  tidy()
aug_2019_ads_dfe_fit
```


### (aug)residual plot(ads VS dfe)
```{r (aug)residual plot(ads VS dfe)}
aug_2019_ads_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ads ~ distance_from_exchange, data = aug_2019_ads_dfe)
aug_2019_ads_dfe_fit_aug  <- augment(aug_2019_ads_dfe_fit$fit)

ggplot(aug_2019_ads_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_ads", y = "Residuals")
```

### (feb) jitter upstream VS dfe
```{r jitter upstream VS dfe}
feb_2019_ju_dfe <- feb_2019_dfe %>%
  select(distance_from_exchange, x24_hour_jitter_upstream) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_ju = mean(x24_hour_jitter_upstream)
  )

feb_2019_ju_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ju ~ distance_from_exchange, data = feb_2019_ju_dfe) %>%
  tidy()
feb_2019_ju_dfe_fit
```


### (feb)residual plot(jitter upstream VS dfe)
```{r residual plot(jitter upstream VS dfe)}
feb_2019_ju_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ju ~ distance_from_exchange, data = feb_2019_ju_dfe)
feb_2019_ju_dfe_fit_aug  <- augment(feb_2019_ju_dfe_fit$fit)

ggplot(feb_2019_ju_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_ju", y = "Residuals")
```


### (aug) jitter upstream VS dfe
```{r (aug)jitter upstream VS dfe}
aug_2019_ju_dfe <- aug_2019_dfe %>%
  select(distance_from_exchange, x24_hour_jitter_upstream) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_ju = mean(x24_hour_jitter_upstream)
  )

aug_2019_ju_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ju ~ distance_from_exchange, data = aug_2019_ju_dfe) %>%
  tidy()
aug_2019_ju_dfe_fit
```


### (aug)residual plot(jitter upstream VS dfe)
```{r (aug)residual plot(jitter upstream VS dfe)}
aug_2019_ju_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_ju ~ distance_from_exchange, data = aug_2019_ju_dfe)
aug_2019_ju_dfe_fit_aug  <- augment(aug_2019_ju_dfe_fit$fit)

ggplot(aug_2019_ju_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_ju", y = "Residuals")
```

### (feb) jitter downstream VS dfe
```{r jitter downstream VS dfe}
feb_2019_jd_dfe <- feb_2019_dfe %>%
  select(distance_from_exchange, x24_hour_jitter_downstream) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_jd = mean(x24_hour_jitter_downstream)
  )

feb_2019_jd_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_jd ~ distance_from_exchange, data = feb_2019_jd_dfe) %>%
  tidy()
feb_2019_jd_dfe_fit
```


### (feb)residual plot(jitter downstream VS dfe)
```{r residual plot(jitter downstream VS dfe)}
feb_2019_jd_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_jd ~ distance_from_exchange, data = feb_2019_jd_dfe)
feb_2019_jd_dfe_fit_aug  <- augment(feb_2019_jd_dfe_fit$fit)

ggplot(feb_2019_jd_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_jd", y = "Residuals")
```


### (aug) jitter downstream VS dfe
```{r (aug)jitter downstream VS dfe}
aug_2019_jd_dfe <- aug_2019_dfe %>%
  select(distance_from_exchange, x24_hour_jitter_downstream) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_jd = mean(x24_hour_jitter_downstream)
  )

aug_2019_jd_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_jd ~ distance_from_exchange, data = aug_2019_jd_dfe) %>%
  tidy()
aug_2019_jd_dfe_fit
```


### (aug)residual plot(jitter downstream VS dfe)
```{r (aug)residual plot(jitter downstream VS dfe)}
aug_2019_jd_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_jd ~ distance_from_exchange, data = aug_2019_jd_dfe)
aug_2019_jd_dfe_fit_aug  <- augment(aug_2019_jd_dfe_fit$fit)

ggplot(aug_2019_jd_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_jd", y = "Residuals")
```


### (feb) latency VS dfe
```{r (feb)latency VS dfe}
feb_2019_latency_dfe <- feb_2019_dfe %>%
  select(distance_from_exchange, x24_hour_latency) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_latency = mean(x24_hour_latency)
  )

feb_2019_latency_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_latency ~ distance_from_exchange, data = feb_2019_latency_dfe) %>%
  tidy()
feb_2019_latency_dfe_fit
```


### (feb)residual plot(latency VS dfe)
```{r (feb)residual plot(latency VS dfe)}
feb_2019_latency_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_latency ~ distance_from_exchange, data = feb_2019_latency_dfe)
feb_2019_latency_dfe_fit_aug  <- augment(feb_2019_latency_dfe_fit$fit)

ggplot(feb_2019_latency_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_latency", y = "Residuals")
```


### (aug) latency VS dfe
```{r (aug)latency VS dfe}
aug_2019_latency_dfe <- aug_2019_dfe %>%
  select(distance_from_exchange, x24_hour_latency) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_latency = mean(x24_hour_latency)
  )

aug_2019_latency_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_latency ~ distance_from_exchange, data = aug_2019_latency_dfe) %>%
  tidy()
aug_2019_latency_dfe_fit
```



### (aug)residual plot(latency VS dfe)
```{r (aug)residual plot(latency VS dfe)}
aug_2019_latency_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_latency ~ distance_from_exchange, data = aug_2019_latency_dfe)
aug_2019_latency_dfe_fit_aug  <- augment(aug_2019_latency_dfe_fit$fit)

ggplot(aug_2019_latency_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_latency", y = "Residuals")
```


### (feb) packet loss VS dfe
```{r (feb)packet loss VS dfe}
feb_2019_pl_dfe <- feb_2019_dfe %>%
  select(distance_from_exchange, x24_hour_packet_loss) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_pl = mean(x24_hour_packet_loss)
  )

feb_2019_pl_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_pl ~ distance_from_exchange, data = feb_2019_pl_dfe) %>%
  tidy()
feb_2019_pl_dfe_fit
```


### (feb)residual plot(packet loss VS dfe)
```{r (feb)residual plot(packet loss VS dfe)}
feb_2019_pl_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_pl ~ distance_from_exchange, data = feb_2019_pl_dfe)
feb_2019_pl_dfe_fit_aug  <- augment(feb_2019_pl_dfe_fit$fit)

ggplot(feb_2019_pl_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_pl", y = "Residuals")
```


### (aug) packet loss VS dfe
```{r (aug)packet loss VS dfe}
aug_2019_pl_dfe <- aug_2019_dfe %>%
  select(distance_from_exchange, x24_hour_packet_loss) %>%
  group_by(distance_from_exchange) %>%
  summarise(
    avg_pl = mean(x24_hour_packet_loss)
  )

aug_2019_pl_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_pl ~ distance_from_exchange, data = aug_2019_pl_dfe) %>%
  tidy()
aug_2019_pl_dfe_fit
```


### (aug)residual plot(packet loss VS dfe)
```{r (aug)residual plot(packet loss VS dfe)}
aug_2019_pl_dfe_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(avg_pl ~ distance_from_exchange, data = aug_2019_pl_dfe)
aug_2019_pl_dfe_fit_aug  <- augment(aug_2019_pl_dfe_fit$fit)

ggplot(aug_2019_pl_dfe_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted avg_pl", y = "Residuals")
```


### (all) time to load webpage VS ads, latency and packet loss
```{r (all)time to load webpage VS ads, latency and packet loss}
all_2019_tlb_fit <- linear_reg() %>%
  set_engine("glm") %>%
  fit(log(x24_hour_time_to_load_webpage) ~ x24_hr_average_download_speed + x24_hour_latency + x24_hour_packet_loss, data = all_2019) %>%
  tidy()
all_2019_tlb_fit
```


### (all)residual plot(time to load webpage VS ads, latency and packet loss)
```{r (all)residual plot(time to load webpage VS ads, latency and packet loss)}
all_2019_tlb_fit <- linear_reg() %>%
  set_engine("glm") %>%
  fit(log(x24_hour_time_to_load_webpage) ~ x24_hr_average_download_speed + x24_hour_latency + x24_hour_packet_loss, data = all_2019)
all_2019_tlb_fit_aug  <- augment(all_2019_tlb_fit$fit)

ggplot(all_2019_tlb_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted log", y = "Residuals")
```


### All Months - predicting ADS from GDHI
```{r gdhi-24h_download-all}
all_24h_ads_gdhi_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ gdhi_per_head, data = all_gdhi_join) %>%
  tidy()
all_24h_ads_gdhi_fit
```

### All Months - predicting ADS from Urban / Rural
```{r urbanrural-24h_download-all}
all_24h_ads_region_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ urban_rural, data = all_gdhi_join) %>%
  tidy()
all_24h_ads_region_fit
```
### All Months - predicting ADS fom both GDHI and Urban / Rural
```{r both-24h_download-all}
all_24h_ads_both_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ urban_rural + gdhi_per_head, data = all_gdhi_join) %>%
  tidy()
all_24h_ads_both_fit
```

### Trying log model with GDHI

```{r log-gdhi-24h_download-all}
all_24h_ads_gdhi_fit_log <- linear_reg() %>%
  set_engine("lm") %>%
  fit(log(x24_hr_average_download_speed) ~ gdhi_per_head, data = all_gdhi_join) %>%
  tidy()
all_24h_ads_gdhi_fit_log
```

### All Months - predicting ADS from UK Region
```{r region-24h_download-all}
all_24h_ads_region_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(x24_hr_average_download_speed ~ region, data = all_gdhi_join) %>%
  tidy()
all_24h_ads_region_fit
```

### Main Data Analysis - Set Seed and Split - Both Months
```{r setseed-split}
set.seed(1234)
all_gdhi_join_split <- initial_split(all_gdhi_join)
all_gdhi_join_train <- training(all_gdhi_join_split)
all_gdhi_join_test <- testing(all_gdhi_join_split)
```

### Urban/Rural and GDHI vs 24 hour Download Speed - Model setup
```{r variables effect 24h-download }
all_gdhi_join_train_rec <- recipe(x24_hr_average_download_speed ~ urban_rural + gdhi_per_head, data = all_gdhi_join_train) %>%
 step_dummy(all_nominal(), -all_outcomes()) 

all_gdhi_join_train_mod <- linear_reg() %>%
 set_engine('lm')

all_gdhi_join_train_wflow <- workflow() %>% 
 add_model(all_gdhi_join_train_mod) %>% 
 add_recipe(all_gdhi_join_train_rec)

all_gdhi_join_train_fit <- all_gdhi_join_train_wflow %>% 
 fit(data = all_gdhi_join_train)

all_gdhi_join_train_fit
glance(all_gdhi_join_train_fit)$adj.r.squared
```

### Predictions from Model Above
```{r predictions_1}
all_2019_24h_ads_predict <- predict(all_gdhi_join_train_fit, new_data = all_gdhi_join_test) %>%
  bind_cols(all_gdhi_join_test %>% select(x24_hr_average_download_speed, urban_rural, gdhi_per_head))
all_2019_24h_ads_predict 
```