---
title: "Geographical Location and Internet Quality of Life"
subtitle: "IDS 2022 - Workshop Group 31/1 Project"
author: "Team Members - Zhihong Chen, Ryan Hall, Chenyi He, Eric Rogers, Eddie Washbrook"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---



```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here

```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/wallpaper2.jpg"
)
```

# Recap

 - Do geographical location and characteristics have an effect on internet quality of life in the UK? 
 - Feb / Aug 2019 - data.gov.uk - Ofcom
 - GDHI data per region - ONS

---

# Findings

 - We saw trends in the data that exist between location and Internet QOL
 - Not enough data to be able to back up this link
 - Unable to establish a clear/strong connection given the data we had

---

# Choropleth Maps

Ryan

---

# Linear Modelling

Chenyi

---

# Model Accuracy - Residual Plots

Zhihong

---

# Model Accuracy - Residual Plots

Zhihong

---

# Model Training and Prediction

Eddie

---

class: inverse, center, middle

## Thank You

---

